### 2017-04-05 paper/oopsla17-submission/evaluation.tex
expand threats to validity

One threat to validity associated with supervised machine learning is
overfitting (\ie learning a model that is too complex with respect to the
data). We mitigate this threat by having separate training and testing
datasets (section FIXME) and via cross-validation (section
FIXME)~\cite{FIXME}.

FIXME threat associated with benchmarks that are not indicative. We
mitigate this threat by including the largest empirical evaluation we are
aware of (re-quote number of program pairs) from two different semesters of
students (re-quote number of students). FIXME note that we ack that
students are not indicative of industrial programmers, but the goal of this
paper is to help novices, since they find type inference errors to be the
most cryptic~\cite{FIXME}.

FIXME threat associated with removing from the dataset program pairs
that change everything or where our parser cannot find nodes corresponding
to the other tools or whatever. FIXME Note that the former is
standard or otherwise similar to previous work~\cite{FIXME}. FIXME note tha
the latter actually helps the state of the art, and anyway our victory
margins are so large that even if assumed they were perfect on all of those
and we were not, we'd still win (double check that math).

FIXME threat associated with using just OCaml instead of Haskell, Reason,
whatever. FIXME admits comparison with previous work, FIXME our functional
subset of ocaml is basically haskell anyway, FIXME Algorithm W is the same
for all of them.

>>>>

One threat to validity associated with supervised machine learning is
overfitting (\ie learning a model that is too complex with respect to
the data).
%
We mitigate this threat by having separate training and testing datasets
(\autoref{sec:quantitative}) and via cross-validation
(~\autoref{sec:feature-utility})~\cite{FIXME}.

Our benchmarks were drawn from students in an undergraduate course and
may not be representative of other student populations.
%
We mitigate this threat by including the largest empirical evaluation of
type error localization that we are aware of: over 4,500 pairs of
ill-typed programs and fixes from two instances of the course, with
programs from 102\ES{TODO: check} different students.
%
We acknowledge, of course, that students are not industrial programmers
and our results may not translate to large-scale software development;
however, we are particularly interested in aiding novice programmers
as they learn to work inside the type system.

Our removal of program pairs that changed too much, where our oracle
could not identify the blame of the other tools, or where the other
tools timed out or encountered unsupported language features is another
threat to validity.
%
It is possible that including the programs that changed excessively
would hurt our models, or that the other tools would perform
better on the programs with unsupported language features.
%
We note however that
%
(1) outlier removal is a standard technique in machine learning
\ES{CITE?}; and
%
(2) our Top-1 accuracy margin is large enough that even if we assumed
that \sherrloc were perfect on all of the excluded programs, it would
only tie our \hiddenFH in Top-1 accuracy.
%
\ES{I think this is accurate, but should double check..}

Examining programs written in \ocaml as opposed to \haskell or any other
language poses another threat to validity, common type errors may differ
in different languages.
%
\ocaml is, however, a standard target for research in type error
localization and thus our choice admits a direct comparison with prior
work.
%
Furthermore, the functional core of \ocaml that we support does not
differ significantly from the functional core of \haskell or SML, all of
which are effectively lambda calculi with a Hindley-Milner-style type
system.\footnote{\haskell's type classes are a notable exception, they
  are also known to cause confusing type errors and would be interesting
  to study in future work.}

Finally, our use of student fixes as oracles for the source of type
errors assumes that, on average, students are able to correctly identify
the source of an error.
%
As the students are in the process of learning the language and type
system, this assumption may be faulty.
%
It may be that \emph{expert} users would disagree with many of the
student fixes, and that it is harder to learn a model of expert fixes,
or that the state of the art would be better at predicting expert fixes.
%
As we have noted before, we believe it is reasonable to use student
fixes as oracles because the student is the best judge of what she
\emph{meant} to do.
